\huge Tor's Usability for Censorship Circumvention

### 2016-05-08 pets2017-paper/pets2017-paper.tex
update time spent on proxy screen in observations

% impacts of making the proxy page ``automated'' 
\item {\bfseries Users wasted time configuring proxies.} This confusion prevented users from configuring their bridges correctly. Participants with the new interface (which explicitly states that they did not need a proxy) spent 31\% of their active time configuring proxies, perhaps due to not reading the text or not believing the interface. Participants in the old interface spent 63\% of their time on the proxy screen. We do not understand why users with the new interface chose to configure proxies after explicitly being told that they do not need one.

>>>>

% impacts of making the proxy page ``automated'' 
\item {\bfseries Users wasted time configuring proxies.} This confusion prevented users from configuring their bridges correctly. Participants with the new interface (which explicitly states that they did not need a proxy) spent about the same time configuring proxies as bridges, whereas users with the old interface spent about twice as much time configuring proxies than bridges. We do not understand why users with the new interface spent time configuring proxies after explicitly being told that they do not need one.
